---
title: "Shapes analysis"
output:
  pdf_document: 
    fig_width: 12
    fig_height: 6
  html_document: default
editor_options: 
  chunk_output_type: console
---

## Analyzing existing shape files and their usefulness


```{r eval = TRUE, echo = FALSE}
conflictRules("tidyr", mask.ok = c("extract"))
conflictRules("dplyr", mask.ok = c("filter", "lag", "select"))
pacman::p_load(sf, raster, stars, rgdal, here, fs, tidyverse, dplyr,  ggpubr,
               writexl, scales, esri2sf, glue, rlang, kableExtra, ggspatial)
theme_set(ggplot2::theme_minimal())
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = T)
source("R/gis-helpers.R")
```


## UNDP-OCHA shapes for somalia

Sources: 

-  [https://data.humdata.org/dataset/somalia-administrative-boundaries](https://data.humdata.org/dataset/somalia-administrative-boundaries)
-  Shared folder `WBG\Takaaki Masaki - somalia\input\admin\som-administrative-divisions-shapefiles`

```{r}
from_fold <- 
  here("data-raw", "shps", "undp-ohca", 
       "som-administrative-divisions-shapefiles")

undp_admin0 <- sf::read_sf(file.path(from_fold, "Som_Admbnda_Adm0_UNDP.shp"))
undp_admin1 <- sf::read_sf(file.path(from_fold, "Som_Admbnda_Adm1_UNDP.shp"))
undp_admin2 <- sf::read_sf(file.path(from_fold, "Som_Admbnda_Adm2_UNDP.shp"))

ggplot() +
  geom_sf(data = undp_admin2, alpha = 0.1, aes(colour = "Admin 2")) + 
  geom_sf(data = undp_admin1, alpha = 0.1, aes(colour = "Admin 1")) +
  geom_sf(data = undp_admin0, alpha = 0.1, aes(colour = "Admin 0")) 
```


## WB Villages data

Source: 

- [https://datacatalog.worldbank.org/dataset/somalia-villages](https://datacatalog.worldbank.org/dataset/somalia-villages)


```{r}
wb_vilages <- 
  here("data-raw",
       "shps",
       "wb-villages",
       "table1_villages.shp_",
       "Table1_Villages.shp") %>%
  sf::read_sf()

som_hex <- 
  undp_admin0 %>%
  st_make_grid(cellsize = .25, square = FALSE)

ggplot() +
  geom_sf(data = undp_admin2, alpha = 0.1, aes(colour = "Admin 2")) + 
  geom_sf(data = undp_admin1, alpha = 0.1, aes(colour = "Admin 1")) +
  geom_sf(data = undp_admin0, alpha = 0.1, aes(colour = "Admin 0")) +
  geom_sf(data = wb_vilages, aes(colour = "Villages"), size = .01)
```


## Geopode - Somaliland and 

Source: 

- [https://son.geopode.world/geometry_export/0/](https://son.geopode.world/geometry_export/0/)

Existing layers in the data:

```{r}
geopode_file <- here("data-raw", "shps", "geopode", "GEOPODE_SON.gdb")
st_layers(geopode_file)
```

First - geometries of the Somaliland and Puntland regions. Several observations: 

- Very fluid borders.
- Regional boundaries of Somaliland and Puntland do not correspond to the country boundaries from the UNDP.
- Internal borders between Puntland and UNDP Zones are also fluid.

```{r warning=FALSE}
geopode_adm1 <- sf::read_sf(geopode_file, layer = "boundary_vacczones")
geopode_adm2 <- sf::read_sf(geopode_file, layer = "boundary_vaccregions")
geopode_adm3 <- sf::read_sf(geopode_file, layer = "boundary_vaccdistricts")

ggplot() +
  geom_sf(data = geopode_adm3, alpha = 0.1, aes(colour = "Admin 3")) + 
  geom_sf_text(data = geopode_adm2, aes(colour = "Admin 2", label = RegionName)) + 
  geom_sf(data = geopode_adm2, alpha = 0.1, aes(colour = "Admin 2")) +
  geom_sf_text(data = geopode_adm1, aes(colour = "Admin 1", label = ZoneName)) + 
  geom_sf(data = geopode_adm1, alpha = 0.1, aes(colour = "Admin 1")) + 
  geom_sf(data = undp_admin1, aes(colour = "UNDP Admin 1"), alpha = 0) + 
  geom_sf(data = undp_admin0, aes(colour = "UNDP Admin 0"), alpha = 0)
```


### Others: health and water


```{r}
geopode_health <- sf::read_sf(geopode_file,  layer = "fc_poi_health_facilities")
geopode_water <- sf::read_sf(geopode_file,  layer = "fc_poi_water")

ggplot() +
  geom_sf(data = geopode_health, aes(colour = "health"), size = 0.5) +
  geom_sf(data = geopode_water, aes(colour = "water"), size = 0.5) +
  geom_sf(data = geopode_adm3, alpha = 0, colour = "blue") + 
  geom_sf(data = geopode_adm2, alpha = 0, colour = "red") +
  geom_sf(data = geopode_adm1, alpha = 0, colour = "black")

```

### Others: Built-up areas and Hamlets

```{r}
geopode_builtup <- sf::read_sf(geopode_file, layer = "fe_builtuparea")
geopode_humplet_area <- sf::read_sf(geopode_file, layer = "fe_hamletareas")

ggplot() +
  geom_sf(data = geopode_adm3, alpha = 0, colour = "blue") + 
  geom_sf(data = geopode_adm2, alpha = 0, colour = "red") +
  geom_sf(data = geopode_adm1, alpha = 0, colour = "black") + 
  geom_sf(data = geopode_builtup, aes(fill = "Build-up", colour = "Build-up")) + 
  geom_sf(data = geopode_humplet_area, aes(fill = "Hamlets", colour = "Hamlets"))
```


## GRID3 

Sources:

- [https://data.humdata.org/dataset/grid3-somalia-settlement-extents-version-01-alpha](https://data.humdata.org/dataset/grid3-somalia-settlement-extents-version-01-alpha)
- Same as [https://academiccommons.columbia.edu/doi/10.7916/d8-4n5t-wd59](https://academiccommons.columbia.edu/doi/10.7916/d8-4n5t-wd59)
-  Also availabie through an API: [Landing page](https://www.arcgis.com/home/item.html?id=958addcc83804d83a5cf795c9b8499f1&view=list&sortOrder=desc&sortField=defaultFSOrder) and the [features server](https://services3.arcgis.com/BU6Aadhn6tbBEdyk/ArcGIS/rest/services/GRID3_SOM_settlement_extents_20200330_V02_gdb/FeatureServer)


Existing layers in the data:

- built up areas (BUA), 
- small settlement areas (SSA), 
- hamlets (hamlets)

```{r}
grid3_file <- here("data-raw", "shps", "grid3",
                     "GRID3_SOM_settlement_extents_20200330_V02.gdb")
st_layers(grid3_file)
```

As the number of hamlets is very large, we do not plot them.

```{r}
grid3_bua <- 
  sf::read_sf(grid3_file, layer = "bua_extents")%>%
  st_cast("MULTIPOLYGON") %>% 
  st_make_valid()
grid3_ssa <- 
  sf::read_sf(grid3_file, layer = "ssa_extents") %>%
  sf::st_cast("MULTIPOLYGON") %>% 
  sf::st_make_valid()
# grid3_ham <- 
#   sf::st_read(grid3_file, layer = "hamlet_extents") %>% 
#   sf::st_cast("MULTIPOLYGON") %>% 
#   sf::st_make_valid()
# grid3_ham %>% write_rds(here("data-raw", "shps", "grid3", "hamlets.rds"), compress = "gz")
grid3_ham <- read_rds(here("data-raw", "shps", "grid3", "hamlets.rds"))

ggplot() +
  geom_sf(data = grid3_bua, alpha = 0.3, aes(colour = "GRID3 BUA" , fill = "GRID3 BUA")) + 
  geom_sf(data = grid3_ssa, alpha = 0.1, aes(colour = "GRID3 SSA" , fill = "GRID3 SSA")) +
  # geom_sf(data = grid3_ham, alpha = 0.1, aes(colour = "GRID3 Hamlets" , fill = "GRID3 Hamlets")) +
  geom_sf(data = undp_admin1, aes(colour = "UNDP Admin 1"), alpha = 0) + 
  geom_sf(data = undp_admin0, aes(colour = "UNDP Admin 0"), alpha = 0)
```



## Poverty map - Does not contain any boundaties

```{r eval=FALSE}
povmap_path <- here("data-raw", "poverty", "SOM_UR_EAs", "SOM_UR_EAs_06.shp")
povmap_shps <- read_sf(povmap_path)
```


## Ideas for merging data together


### Discarded 

Was discarded because of the unofficial and undocumented nature of the GEOPODE data and limited improvement of the boundaries precision. 

1. Use Geopode for Somaliland and Puntland Admin 1 - zones, Admin 2 - regions and Admin 3 - districts as it is. 
2. Combine Geopode with the UNDP boundaries for Admin 0 - Country, Admin 1 - Zone and Admin 2 - Region by: 

   -  Using external Admin 1 boundaries from Geopode to "improve" accuracy of UNDP Admin 0 - country boundaries.
   -  Remove Geopode regions from UNDP Admin 1 and Admin 2 regions. 
   -  Create artificial layer Admin 3 in UNDP data using hexagons to dis-aggregate every Admin 2 region to the artificial Admin 3 districts. 
   
3. If we need to use Village boundaries or hamlets, explore further if we can use Geopode in a combination with GRID3 or need to go for one of it.  
 


### Accepted temporary solution

1. UNDP for Admin 0, 1, and 2.

2. Geopode for Admin 3 in the North and in the rest, Admin 3 is the same as Admin 2.


```{r}
zam_geom <- read_rds("../../zambia/zamPTIapp/app-shapes/Zambia.rds")
zam_geom$admin0_Country

som_geom <- NULL

som_geom$admin0_Country <-
  undp_admin0 %>%
  mutate(area = st_area(.),
         area = as.numeric(area) / 1000000) %>%
  select(admin0Name, admin0Pcod, area) %>%
  st_cast("MULTIPOLYGON") %>%
  st_make_valid()

som_geom$admin1_Region <- 
  undp_admin1 %>%
  mutate(area = st_area(.),
         area = as.numeric(area) / 1000000) %>%
  select(admin0Pcod, admin1Name, admin1Pcod, area) %>%
  arrange(admin1Pcod) %>% 
  st_cast("MULTIPOLYGON") %>%
  st_make_valid()

som_geom$admin2_District <- 
  undp_admin2 %>%
  mutate(area = st_area(.),
         area = as.numeric(area) / 1000000) %>%
  select(admin0Pcod, admin1Pcod, admin2Name, admin2Pcod, area) %>%
  arrange(admin2Pcod) %>% 
  st_cast("MULTIPOLYGON") %>%
  st_make_valid()

```


```{r eval=FALSE}
som_geom %>%
  write_rds(here("data-clean", "bounds", str_c(
    "som-geom-undp",
    #as.numeric(Sys.time()), 
    ".rds"
  )),
  compress = "gz")
```

Checking the boundaries

```{r}
som_geom %>% 
  imap_dfr(~{
    .x %>% mutate(id = .y) 
  }) %>% 
  # filter(id != "admin0_Country") %>% 
  ggplot() + 
  geom_sf() + 
  facet_wrap(~id, nrow = 1) + 
  labs(title = "UNDP boundaries")
```


#### Comparing GEOPODE and UNDP borders accuracy

Geopode in fact contains borders that differ from UNDP boundaries, however, this does not improve data granularity as the administrative level remains the same.  

```{r}
som_geom$admin2_District %>%
  ggplot +
  geom_sf() +
  geom_sf(
    data = geopode_adm3,
    alpha = 0,
    linetype = "dashed",
    colour = "red"
  )
```


## Doing hexagons:

We have following sources of SSA and villages data:

[Grid3](https://data.humdata.org/dataset/grid3-somalia-settlement-extents-version-01-alpha) actual polygons of the settlement of 3 different classes. 

- build-up areas.  Polygons number: `r nrow(grid3_bua)`;
- small settlements area. Polygons number: `r nrow(grid3_ssa)`;
- hamlets areas. Polygons number: `r nrow(grid3_ham)`;

[World Bank villages](https://datacatalog.worldbank.org/dataset/somalia-villages) contains points, where the villages are located. In total {r nrow(wb_vilages)} points.

[Geopode](https://son.geopode.world/geometry_export/0/) only covers two regions on the north. 

- Build-up areas as polygons. Total of {r nrow(geopode_builtup)} BUAs.
- Hamlets extents as circles of a fixed radius for all hamlets. Total of {r nrow(geopode_humplet_area)} hamlets

```{r fig.width=16, fig.height=7}
focus_box <- c(xmin = 43.98, xmax = 44.1, ymin = 9.5, ymax = 9.64)

geopode_dta <-
  geopode_humplet_area %>% mutate(type = "hamlet") %>% 
  bind_rows(geopode_builtup %>% mutate(type = "bua")) %>% 
  st_crop(., focus_box) %>% 
  mutate(source = "Geopode") %>% 
  ggplot() + 
  ggspatial::annotation_map_tile(zoom = 13, 
                                 cachedir = here("data-raw", "osm-tiles"), 
                                 interpolate = T) + 
  geom_sf(aes(fill = type), alpha = 0.2) +
  labs(title = "Geopode") +
  theme(legend.position="bottom")

grid3_dta <-
  list(
    grid3_bua, 
    grid3_ssa, 
    grid3_ham %>% st_crop(., focus_box)
    ) %>%
  bind_rows()  %>% 
  st_crop(., focus_box) %>% 
  mutate(source = "GRID3") %>% 
  ggplot() + 
  ggspatial::annotation_map_tile(zoom = 13, 
                                 cachedir = here("data-raw", "osm-tiles"), 
                                 interpolate = T) + 
  geom_sf(aes(fill = type), alpha = 0.2) +
  labs(title = "GRID3") +
  theme(legend.position="bottom")

wb_dta <-
  wb_vilages %>%
    st_transform(st_crs(grid3_bua)) %>% 
  st_crop(., focus_box) %>%
  mutate(source = "WB", type = "Village") %>% 
  ggplot() + 
  ggspatial::annotation_map_tile(zoom = 13, 
                                 cachedir = here("data-raw", "osm-tiles"), 
                                 interpolate = T) + 
  geom_sf(aes(fill = type), alpha = 1, size = 4) +
  labs(title = "WB Villages") +
  theme(legend.position="bottom")

ggpubr::ggarrange(
  geopode_dta,
  grid3_dta,
  wb_dta,
  nrow = 1,
  ncol = 3
)
```

Based on the images, it is clear that GRID3 data outperforms the other sources. Therefore, we could use it as a reference point. 

% of the WB villages is withing the GRID 3 boundaries.  


```{r echo=FALSE}
# % of the WB villages is withing the GRID 3 boundaries.  
# library(rmapshaper)
# 
# grid3_combined <-
#   list(grid3_bua,
#        grid3_ssa,
#        grid3_ham) %>%
#   bind_rows()
# 
# wb_vilages_check <-
#   wb_vilages %>%
#   st_transform(st_crs(grid3_bua)) 
# 
# wb_not_in_grid3 <- 
#   wb_vilages_check %>% 
#   ms_erase(grid3_ssa)
# 
# wb_not_in_grid3_2 <- 
#   wb_not_in_grid3  %>% 
#   ms_erase(grid3_bua)
#   
# wb_not_in_grid3_3 <- 
#   wb_not_in_grid3_2 %>% 
#   ms_erase(grid3_ham)
# 
# wb_in_grid3 <- 
#   st_intersects(
#   wb_vilages_check, 
#   grid3_combined
# ) 
# wb_in_grid3_extended <- 
#   st_is_within_distance(
#   wb_vilages_check, 
#   grid3_combined, 
#   dist = 1
# ) 

```

```{r echo=FALSE}
# library(rmapshaper)
# 
# grid3_combined <-
#   list(grid3_bua,
#        grid3_ssa,
#        grid3_ham) %>%
#   bind_rows()

# one_subregion <-
#   som_geom$admin2_District %>% 
#   slice(42)
# 
# one_grid3_region <- 
#   grid3_combined %>% 
#   st_crop(one_subregion) %>% 
#   st_intersection(one_subregion)
# 
# 
# one_subregion %>%
#   st_make_grid(cellsize = .15, square = FALSE, flat_topped = T) %>% 
#   ggplot() + 
#   geom_sf() + 
#   geom_sf(data = one_grid3_region, aes(fill = type)) +
#   geom_sf(data = one_subregion, alpha = 0.1)

# 
#   map_dfr( ~ {
#     full_grid %>%
#       st_intersection(.x) %>%
#       st_cast("MULTIPOLYGON") %>%
#       st_make_valid() %>%
#       mutate(
#         rnn = row_number() %>% as.character(),
#         rnn = ifelse(nchar(rnn) == 1, str_c("0", rnn), rnn),
#         admin3Pcod = str_c(admin2Pcod, rnn),
#         admin3Name = str_c(admin2Name, " (", rnn, ")"),
#         area = st_area(.) %>% as.numeric(),
#         area = area / 1000000
#       ) %>%
#       select(admin0Pcod, admin1Pcod, admin2Pcod, admin3Pcod, admin3Name,
#              area, geometry)
#   })


```


```{r eval=FALSE}
# Possible alternative approachse: 
# 
# -  Explore how point data could be polygonized in the meaningful polygons that 
#    combine villages densities.
# -  See: `gstat::krige` and `sp::aggregate` help files and documentation as 
#    well as [fields](https://cran.r-project.org/web/packages/fields/fields.pdf) R package.
 
full_grid <- 
  som_geom$admin0_Country %>% 
  st_make_grid(cellsize = .15, square = FALSE, flat_topped = T) %>% 
  st_as_sf() %>% 
  rename(geometry = x)  

som_geom2 <- som_geom

# Identifying polygons corresponding to each hexagon
som_geom2$admin3_Hexagons <-
  full_grid %>%
  mutate(grid_id = row_number()) %>%
  get_intercestions(som_geom$admin2_District) %>%
  group_by(grid_id) %>%
  arrange(desc(area_under)) %>%
  slice(1) %>%
  ungroup() %>% 
  left_join(full_grid %>% mutate(grid_id = row_number())) %>% 
  st_as_sf() %>% 
  rmapshaper::ms_clip(som_geom2$admin0_Country) %>% 
  st_make_valid() %>%
  group_by(admin2Pcod) %>%
  mutate(
    rnn = row_number() %>% as.character(),
    rnn = ifelse(nchar(rnn) == 1, str_c("0", rnn), rnn),
    admin3Pcod = str_c(admin2Pcod, rnn),
    admin3Name = str_c(admin2Name, " (", rnn, ")"),
  ) %>%
  ungroup() %>%
  select(admin0Pcod,
         admin1Pcod,
         admin2Pcod,
         admin3Pcod,
         admin3Name,
         area,
         geometry) 

# # # Cutting hexagons into parts.
# individual_polys <- 
#   som_geom$admin2_District %>% 
#   group_by(row_number()) %>% 
#   nest() %>% 
#   pull(data) %>% 
#   map(~st_make_valid(.x))
# 
# som_geom2$admin3_Hexagons <- 
#   individual_polys %>%
#   map_dfr( ~ {
#     full_grid %>%
#       st_intersection(.x) %>%
#       st_cast("MULTIPOLYGON") %>%
#       st_make_valid() %>%
#       mutate(
#         rnn = row_number() %>% as.character(),
#         rnn = ifelse(nchar(rnn) == 1, str_c("0", rnn), rnn),
#         admin3Pcod = str_c(admin2Pcod, rnn),
#         admin3Name = str_c(admin2Name, " (", rnn, ")"),
#         area = st_area(.) %>% as.numeric(),
#         area = area / 1000000
#       ) %>%
#       select(admin0Pcod, admin1Pcod, admin2Pcod, admin3Pcod, admin3Name,
#              area, geometry)
#   })


# som_geom2 %>% devPTIapp::validate_geometries()

som_geom2 %>% 
  write_rds(here("data-clean", "bounds", "som-geom-undp-hexagons.rds"), compress = "gz")

som_geom2 %>% 
  iwalk(~{
    to <- str_c("./data-clean/som-shapefiles/", .y)
    dir.create(to, showWarnings = F, recursive = T)
    to <- str_c(to, "/", .y, ".shp")
    st_write(.x, to, delete_dsn = TRUE, delete_layer = TRUE )
  })
```

```{r}
som_geom2 <- here("data-clean", "bounds", "som-geom-undp-hexagons.rds") %>% read_rds()

som_geom2$admin3_Hexagons %>%
  ggplot() +
  geom_sf(alpha = 0.1) +
  geom_sf(
    data = som_geom2$admin2_District,
    alpha = 0,
    colour = "red"
  ) +
  geom_sf(
    data = geopode_adm3,
    alpha = 0,
    linetype = "dashed",
    colour = "blue"
  )
```


## Build-up area in each region/hexagon


```{r eval=FALSE}
# grid3_combined <-
#   list(grid3_bua,
#        grid3_ssa,
#        grid3_ham) %>%
#   bind_rows() %>%
#   # st_union() %>%
#   st_transform(st_crs(wb_vilages))# %>% 
#   # st_make_valid()
# 
# grid3_combined %>%
#   write_rds("data-raw/shps/grid3/grid3_combined.rds", compress = "gz")

grid3_combined <- read_rds("data-raw/shps/grid3/grid3_combined.rds")

# library(progress)
# pb <-
#   progress::progress_bar$new(
#   format = "[:bar] :percent eta: :eta",
#   show_after = 1,
#   total = som_geom2 %>% map_dfr(st_drop_geometry) %>% nrow())

existing <-
  here("data-raw", "temp", "grid3-areas") %>% 
  list.files(pattern = "rds") %>% 
  str_replace_all("\\.rds", "")

bua_area_grid3 <- 
  som_geom[3] %>% 
  imap(~{
    adm_level <- str_extract(.y, "admin\\d")
    var_name <- str_c("bua_area_grid3_", adm_level)
    out <- nrow(.x)
    .x %>% 
      st_transform(st_crs(wb_vilages)) %>% 
      group_by(row_number()) %>% 
      nest() %>% 
      pull(data) %>% 
      # `[`(1:5) %>% 
      map2_dfr(seq_along(.), ~{
        cat(scales::percent(.y / out, accuracy = 0.1), "\n")
        if (.x$admin2Pcod %in% existing) {
          here("data-raw",
               "temp",
               "grid3-areas",
               str_c(.x$admin2Pcod, ".rds")) %>%
            read_rds() %>%
            return()
        } else {
          one_reg_bua <-
            grid3_combined %>%
            st_crop(.x) %>% 
            st_union() %>% 
            st_intersection(.x) %>% 
            st_area() %>%
            as.numeric()
          
          if (identical(one_reg_bua, numeric(0))) {
            one_reg_bua <- 0
          }
          out <-
            .x %>%
            st_drop_geometry() %>%
            as_tibble() %>%
            mutate({{var_name}} := one_reg_bua / 1000000)
          write_rds(out, here(
            "data-raw",
            "temp",
            "grid3-areas",
            str_c(out$admin2Pcod, ".rds")
          ), compress = "gz")
          out
        }
    })
  })

bua_area_grid3 <- NULL

bua_area_grid3$admin2_District <- 
  here("data-raw", "temp", "grid3-areas") %>% 
  list.files(pattern = "rds", full.names = T) %>% 
  map_dfr(read_rds)

bua_area_grid3 <-
  bua_area_grid3$admin2_District %>% 
  select(-area) %>% 
  group_by(admin0Pcod, admin1Pcod) %>% 
  summarise(across(where(is.numeric), ~sum(., na.rm = TRUE))) %>% 
  ungroup() %>% 
  left_join(som_geom$admin1_Region) %>% 
  select(-geometry) %>% 
  as_tibble() %>% 
  select(contains("admin0"), contains("admin1"), area, everything()) %>% 
  list(admin1_Region = .) %>% 
  append(., bua_area_grid3)

bua_area_grid3 <-
  bua_area_grid3$admin2_District %>% 
  select(-area) %>% 
  group_by(admin0Pcod) %>% 
  summarise(across(where(is.numeric), ~sum(., na.rm = TRUE))) %>% 
  ungroup() %>% 
  left_join(som_geom$admin0_Country) %>% 
  select(-geometry) %>% 
  as_tibble() %>% 
  select(contains("admin0"), area, everything()) %>% 
  list(admin1_Region = .) %>% 
  append(., bua_area_grid3)

bua_area_grid3 <- 
  bua_area_grid3 %>% 
  map(~.x %>% select(-area))
  
bua_area_grid3 %>% 
  write_rds(here("data-clean", "som-bua-in-reg-grid3.rds"), compress = "gz")
```

```{r}
bua_area_grid3 <- 
  here("data-clean", "som-bua-in-reg-grid3.rds") %>% 
  read_rds()

all_plots <-
  bua_area_grid3 %>%
  imap(~ {
    .x %>%
      plot_admin_level_ggmap(geometries = som_geom)
  })

# all_plots[2:3] %>% 
#   ggarrange(plotlist = ., nrow = 1)
```

```{r eval=FALSE}
# Converting hexagons
existing <-
  here("data-raw", "temp", "grid3-areas-hexes") %>% 
  list.files(pattern = "rds") %>% 
  str_replace_all("\\.rds", "")

bua_area_grid3_hexes <- 
  som_geom2[4] %>% 
  imap(~{
    adm_level <- str_extract(.y, "admin\\d")
    var_name <- str_c("bua_area_grid3_", adm_level)
    out <- nrow(.x)
    .x %>% 
      st_transform(st_crs(wb_vilages)) %>% 
      group_by(row_number()) %>% 
      nest() %>% 
      pull(data) %>% 
      map2_dfr(seq_along(.), ~{
        cat(scales::percent(.y / out, accuracy = 0.1), "\n")
        if (.x[[str_c(adm_level, "Pcod")]] %in% existing) {
          here("data-raw", "temp", "grid3-areas-hexes",
               str_c(.x[[str_c(adm_level, "Pcod")]], ".rds")) %>%
            read_rds() %>%
            return()
        } else {
          one_reg_bua <-
            grid3_combined %>%
            st_crop(.x) %>% 
            st_union() %>% 
            st_intersection(.x) %>% 
            st_area() %>%
            as.numeric()
          # pb$tick()
          if (identical(one_reg_bua, numeric(0))) {
            one_reg_bua <- 0
          }
          out <-
            .x %>%
            st_drop_geometry() %>%
            as_tibble() %>%
            mutate({{var_name}} := one_reg_bua / 1000000)
          write_rds(out, here(
            "data-raw",
            "temp",
            "grid3-areas-hexes",
            str_c(out[[str_c(adm_level, "Pcod")]], ".rds")
          ), compress = "gz")
          out
        }
    })
  })

bua_area_grid3_hexes <- bua_area_grid3

bua_area_grid3_hexes$admin3_Hexagons <- 
  here("data-raw", "temp", "grid3-areas-hexes") %>% 
  list.files(pattern = "rds", full.names = T) %>% 
  map_dfr(read_rds) %>% 
  select(-area)

bua_area_grid3_hexes %>% 
  write_rds(here("data-clean", "som-bua-in-reg-grid3-hexagons.rds"), compress = "gz")

```


```{r}
bua_area_grid3_hexes <- 
  here("data-clean", "som-bua-in-reg-grid3-hexagons.rds") %>% 
  read_rds()

all_plots2 <-
  bua_area_grid3_hexes %>%
  imap(~ {
    .x %>%
      plot_admin_level_ggmap(geometries = som_geom2)+ 
      labs(title = .y)
  })

all_plots2[2:4] %>%
  ggarrange(plotlist = ., nrow = 1)
```


## Build-up area as a fraction of total area in each region/hexagon


```{r}
bua_area_grid3_hexes %>%
  imap(~{
    .x %>%
      left_join(som_geom2[[.y]]) %>%
      select(-geometry) %>%
      # st_drop_geometry() %>%
      as_tibble() %>%
      mutate_at(vars(contains("bua_area_grid3")), list(~ . / area * 100))
  }) %>%
  imap(~ {
    .x %>%
      plot_admin_level_ggmap(geometries = som_geom2) + 
      labs(title = .y)
  }) %>%
  `[`(2:4) %>%
  ggarrange(plotlist = ., nrow = 1)



```

